Inventor Disambiguation Report

### 2022-05-20 examples/benchmark/full-report.qmd
update

---
title: Inventor Disambiguation Report
format:
    html:
        theme: cosmo
        code-fold: true
        code-tools: true
        code-block-border-left: true
        code-copy: true
        code-block-border-left: "#31BAE9"
jupyter: python3
---

## Data Preparation

@@

Mention IDs are standardized to be of the form `<OFFICE><PATENT_NUMBER>-<INVENTOR_SEQUENCE>`, where OFFICE is the patent issuer office abbreviation (e.g. "US" or "EPO"), PATENT_NUMBER is the standard patent number form, and INVENTOR_SEQUENCE is the inventor's position on the given patent, starting from 0. For example, the mention ID
> US5811073-0
represents the first listed inventor on US patent number 5811073.

```{python}
#| label: data-prep
#| code-fold: true
import pandas as pd

@@

Next, we define a dictionary describing the two disambiguations to compare, i.e. the "current" disambiguation and the "one cluster" trivial disambiguation.

@@

We can now generate the disambiguation report using `disambiguations` and `rawinventor.tsv` as the input.

@@

from pv_evaluation.summary import InventorDisambiguationSummary

@@

@@

@@

@@

@@

@@

@@

>>>>

---
title: Inventor Disambiguation Report
format:
    html:
        theme: cosmo
        code-fold: true
        code-tools: true
        code-block-border-left: true
        code-copy: true
        code-block-border-left: "#31BAE9"
        echo: false
        include-in-header: header.html
        include-after-body: footer.html
execute:
  cache: true
  warning: false
  message: false
jupyter: python3
---

<!--
## Data Preparation

@@

Mention IDs are standardized to be of the form `<OFFICE><PATENT_NUMBER>-<INVENTOR_SEQUENCE>`, where OFFICE is the patent issuer office abbreviation (e.g. "US" or "EPO"), PATENT_NUMBER is the standard patent number form, and INVENTOR_SEQUENCE is the inventor's position on the given patent, starting from 0. For example, the mention ID
> US5811073-0
represents the first listed inventor on US patent number 5811073.
-->
```{python}
#| label: data-prep
#| code-fold: true
import pandas as pd

@@

<!--
Next, we define a dictionary describing the two disambiguations to compare, i.e. the "current" disambiguation and the "one cluster" trivial disambiguation.-->

@@

<!--
We can now generate the disambiguation report using `disambiguations` and `rawinventor.tsv` as the input.
-->

@@

from pv_evaluation.summary import InventorDisambiguationSummary
from pv_evaluation.benchmark import inventor_benchmark_plot

@@

::: {.panel-tabset}

### Cluster Sizes

@@

### Top Inventors

@@

### Entropy Curve

@@

### Cluster Homogeneity

@@

### Cluster Separation

@@

:::

@@

::: {.panel-tabset}

### Evaluation Results

```{python}
inventor_benchmark_plot(disambiguations)
```

### Predicted Cluster Errors

::: {.panel-tabset}

#### Israeli Inventors

```{python}
#| column: page
from pv_evaluation.benchmark import (
    load_israeli_inventors_benchmark,
    load_patentsview_inventors_benchmark,
    inspect_clusters_to_split,
    inspect_clusters_to_merge
)

inspect_clusters_to_split(disambiguations["current"], load_israeli_inventors_benchmark()).to_html()
```

#### PatentsView Inventors

```{python}
#| column: page
inspect_clusters_to_split(disambiguations["current"], load_patentsview_inventors_benchmark()).to_html()
```

:::

### Reference Cluster Errors

::: {.panel-tabset}

#### Israeli Inventors

```{python}
#| column: page
inspect_clusters_to_merge(disambiguations["current"], load_israeli_inventors_benchmark()).to_html()
```

#### PatentsView Inventors

```{python}
#| column: page
inspect_clusters_to_merge(disambiguations["current"], load_patentsview_inventors_benchmark()).to_html()
```

:::

:::

## Representative Performance Estimates
